[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/sigmajs.svg?branch=master)](https://travis-ci.org/JohnCoene/sigmajs) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/sigmajs?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/sigmajs)  [![bitbucket](https://img.shields.io/bitbucket/pipelines/JohnCoene/sigmajs.svg)](https://bitbucket.org/JohnCoene/sigmajs) [![CircleCI](https://img.shields.io/circleci/project/github/JohnCoene/sigmajs.svg)](https://github.com/JohnCoene/sigmajs) [![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable) [![CRAN status](https://www.r-pkg.org/badges/version/sigmajs)](https://cran.r-project.org/package=sigmajs) 

```{r, eval=TRUE, echo = FALSE}
library(htmltools)
library(sigmajs)
nodes <- sg_make_nodes(20)
edges <- sg_make_edges(nodes, 30)

# reset size to 1
nodes$size <- 1

# change initial colors
nodes$color <- colorRampPalette(c("#922b29", "#da7d7b"))(nrow(nodes))
 
# add transition
n <- nrow(nodes)
L <- 10

# in circle
nodes$to_x <- 0
nodes$to_y <- 0
for(i in 1:nrow(nodes)){
	nodes$to_x[i] <- L * cos(pi * 2 * i / n - pi / 2)
	nodes$to_y[i] <- L * sin(pi * 2 * i / n - pi / 2)
}

nodes$to_size <- runif(n, 2, 6) # size

# colors
COLORS <- c("#1C5C70", "#B1E2A3")
nodes$to_color <- colorRampPalette(COLORS)(n)
 
# plot
sigmajs(width = "100%", height = 150) %>%
	sg_nodes(nodes, id, size, color, to_x, to_y, to_size, to_color) %>%
	sg_edges(edges, id, source, target) %>% 
	sg_animate(mapping = list(x = "to_x", y = "to_y", size = "to_size", color = "to_color"),
	           delay = 1000) %>%
	sg_settings(animationsTime = 2000) -> net

div(
  class = "row",
  br(),
  br(),
  div(
    class = "col-md-6",
    img(
      src = "man/figures/logo.png",
      class = "img-responsive",
      style = "margin: 0 auto;"
    )
  ),
  div(
    class = "col-md-6",
    net
  )
)
```

[sigmajs](http://sigmajs.org/) for R.

With the rise in popularity of networks, it is important for R users to have access to a package that allows visualising the aforementioned networks in a highly configurable, interactive and dynamic manner. `sigmajs` leverages the [original library](http://sigmajs.org/)'s great many methods by providing numerous proxies, buttons, and more.

All graphs must be initialised with the `sigmajs()` function, all the functions of the package start with `sg_` and its proxies end in `_p`, functions are pipe-friendly (`%>%`).

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-4",
    div(
      class = "thumbnail",
      div(
        class = "caption",
        h3("Get Started"),
        p("Get started with", code("sigmajs"), ", draw your first graphs and learn about settings."),
        p(
          a(
            href = "articles/get_started.html",
            class = "btn btn-primary",
            tags$i(class = "fa fa-rocket"),
            "Get Started"
          ),
          a(
            href = "reference/",
            class = "btn btn-default",
            tags$i(class = "fa fa-book"),
            "Docs"
          )
        )
      )
    )
  ),
  div(
    class = "col-md-4",
    div(
      class = "thumbnail",
      div(
        class = "caption",
        h3("Dynamism"),
        p("Learn how to make a temporal graph in static R markdown documents."),
        p(
          a(
            href = "articles/dynamic.html",
            class = "btn btn-primary",
            tags$i(class = "fa fa-spinner fa-pulse fa-fw"),
            "Dynamic"
          ),
          a(
            href = "articles/buttons.html",
            class = "btn btn-success",
            tags$i(class = "fa fa-gavel"),
            "Buttons"
          )
        )
      )
    )
  ),
  div(
    class = "col-md-4",
    div(
      class = "thumbnail",
      div(
        class = "caption",
        h3("Shiny"),
        p("Explore the package's proxies and learn how to capture user interactions."),
        p(
          a(
            href = "articles/shiny.html",
            class = "btn btn-primary",
            tags$i(class = "fa fa-graduation-cap"),
            "Guide"
          ),
          a(
            href = "http://shiny.john-coene.com/sigmajs/",
            target = "_blank",
            class = "btn btn-success",
            tags$i(class = "fa fa-desktop"),
            "Demo"
          )
        )
      )
    )
  )
)
```

## Install

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/sigmajs") # github
devtools::install_bitbucket("JohnCoene/sigmajs") # bitbucket
```

## Examples

Most functions have corresponding `demo()`.

*Note that the graphs may not work in RStudio viewer, open them in the browser of your choice.*

```{r, eval=TRUE}
library(sigmajs)

# generate data
nodes <- sg_make_nodes(25) # 20 nodes
edges <- sg_make_edges(nodes, 50) # 50 edges

# visualise
sigmajs() %>%
  sg_nodes(nodes, id, label, size, color) %>%
  sg_edges(edges, id, source, target) %>%
  sg_layout()
```

Most functions have corresponding demos, execute the command in the `run` column to see sigmajs in action. You can also see some of these examples [here](http://shiny.john-coene.com/sigmajs/).

```{r, eval = TRUE, echo = FALSE}
demos <- readLines("./demo/00Index")
demos <- strsplit(demos, "\t+|([[:space:]]){3}")
demos <- demos[lapply(demos, length) > 1]
df <- data.frame()
for(i in 1:length(demos)){
	row <- data.frame(
		name = paste0("`", trimws(demos[[i]][1]), "`"), 
		run = paste0("`demo(", trimws(demos[[i]][1]), ", package='sigmajs')`")
	)
	df <- rbind.data.frame(df, row)
}

knitr::kable(df, caption = "sigmajs demos", format = "html")
```
