# sigmajs

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/sigmajs.svg?branch=master)](https://travis-ci.org/JohnCoene/sigmajs) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/sigmajs?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/sigmajs)

[sigmajs](http://sigmajs.org/) for R.

With the rise in popularity of networks, it is important for R users to have access to a package that allows visualising the aforementioned networks in a highly configurable, interactive and dynamic manner.
`sigmajs` is a [Shiny](https://shiny.rstudio.com/)-centric in order to best leverage the [original library](http://sigmajs.org/)'s great many methods.

All graphs must be initialised with the `sigmajs()` function, all the functions of the :package: start with `sg_` and its proxies end in `_p`, functions are pipe-friendly (`%>%`).

## Install

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/sigmajs")
```

## Examples

Most functions have corresponding `demo()`.

```{r, eval = TRUE}
library(sigmajs)

# generate data
nodes <- sg_make_nodes(25) # 20 nodes
edges <- sg_make_edges(nodes, 50) # 50 edges

# visualise
sigmajs() %>%
	sg_nodes(nodes, id, label, size, color) %>%
	sg_edges(edges, id, source, target)
```

```{r, eval = FALSE}
demo(package = "sigmajs") # proxies and shiny demos
```
