---
title: "Buttons"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Buttons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE
)
library(sigmajs)
```

`sigmajs` lets you add buttons to trigger events, *in static documents*.

A button to export the graph as SVG, not that you can export to an image (png, jpeg, gif or tiff).

```{r}
nodes <- sg_make_nodes() 
edges <- sg_make_edges(nodes)

sigmajs() %>% 
  sg_nodes(nodes, id, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_layout() %>% 
  sg_export_svg() %>% 
  sg_button(
    "<i class='fa fa-download'></i>", 
    "export_svg", # event to trigger
    class = "btn btn-default"
  )
```

You can also trigger mutliple events with the button by passing a vector of events to `event`. Below we add a button that will start the forceAtlas2 layout and stop it after 3 seconds. 

```{r}
sigmajs() %>% 
  sg_nodes(nodes, id, size, color) %>% 
  sg_edges(edges, id, source, target) %>% 
  sg_force_start() %>% 
  sg_force_stop(3000) %>% 
  sg_button(
    "<i class='fa fa-play'></i> Layout", # only use icon if document imports fontawesome
    c("force_start", "force_stop"), 
    class = "btn btn-success"
  )
```

Events that can be triggered via a button (corresponding function name minus `sg_`):

* `force_start`
* `force_stop`
* `noverlap`
* `drag_nodes`
* `relative_size`
* `add_nodes`
* `add_edges`
* `add_nodes_edges`
* `drop_nodes`
* `drop_edges`
* `animate`
* `export_svg`
* `export_img`

You will examples of the above scattered throughout the documentation.