---
title: "Dynamic graphs"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dynamic graphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(sigmajs)
```

You also add nodes and edges to static graphs. Below we graph the nodes then add (`sg_add_edges`) at random intervals (0.5 to 2 seconds *between* each edge added). We also stop the layout algorithm after all edges have been aded (+ 100 milliseconds to be on the safe side).

*Note that by the time you reach the bottom of the page all edges will likely be plotted already, refresh and scroll back here to see it in effect*

```{r}
# generate data using convenience functions
nodes <- sg_make_nodes(50)
edges <- sg_make_edges(nodes)
edges$delay <- runif(15, 500, 2000) # between .5 and 2 seconds

last_edge <- sum(edges$delay) + 100

sigmajs() %>%
  sg_force_start() %>%
  sg_nodes(nodes, id, size, color) %>%
  sg_add_edges(edges, delay, id, source, target) %>% # read delay documentation
  sg_force_stop(last_edge)
```

You can also drop nodes or edges with `sg_drop_edges` and `sg_drop_nodes`, same principles, I'll let you explore the examples.
