---
title: "Shiny"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(sigmajs)
```

`sigmajs` goes hand in hand with Shiny. As [stated in the wiki](https://github.com/jacomyal/sigma.js/wiki), sigma.js is "interactivity oriented" and therefore plays ideally in apps.

## Features

* Proxies
* Events

`simgajs` lets you dynamically interact with the graph, that is, add/remove/customise without redrawing the whole graph: these functions all end in `_p`. The :package: also lets you catch how the user interacts with your graph.

## Proxies

* Add one or multiple nodes or edges.
* Remove one or multiple nodes or edges.
* Add nodes or edges with a given delay.
* Enable nodes drag.
* Start/kill/restart force layout.
* Refresh the graph.

### Walkthrough

Here I mainly talk you through shiny proxies in general and the `add-nodes` demo.

Let's start by building a simple Shiny app that includes a basic `sigmajs` graph.

```{r, eval = FALSE}
library(shiny)
library(sigmajs)

nodes <- sg_make_nodes()
edges <- sg_make_edges(nodes)

ui <- fluidPage(sigmajsOutput("sg")) # bare bone UI

server <- function(input, output){
  output$sg <- renderSigmajs({
    sigmajs() %>%
      sg_nodes(nodes, id, size, color) %>%
      sg_edges(edges, id, source, target)
  })
}

shinyApp(ui, server) # run
```

Now that we have a simple app going we can look at playing with proxies. The layout looks a bit rubbish, we can add a proxy to let the user trigger the forceAtlas2 layout.

```{r, eval = FALSE}
nodes <- sg_make_nodes()
edges <- sg_make_edges(nodes)

ui <- fluidPage(
  actionButton("start", "Trigger layout"), # add the button
  sigmajsOutput("sg")
) 

server <- function(input, output){

  output$sg <- renderSigmajs({
    sigmajs() %>%
      sg_nodes(nodes, id, size, color) %>%
      sg_edges(edges, id, source, target)
  })

  observeEvent(input$start, {
    sigmajsProxy("sg") %>% # use sigmajsProxy!
      sg_force_start_p() # app the proxy (_p)
  })

}

shinyApp(ui, server) # run
```

So proxies work on a already existing graphs so you simply have to use the `sigmajsProxy` function to catch that graph using its `id`; output graph's id is `sg` (`sigmajsOutput("sg")`). Then you can pass your proxies `_p`.

We could, for instance, now add another button to kill the layout because as it is now the layour is constantly running which is a bit draining for the browser and not very useful.

```{r, eval = FALSE}
nodes <- sg_make_nodes()
edges <- sg_make_edges(nodes)

ui <- fluidPage(
  actionButton("start", "Start layout"), # start button
  actionButton("stop", "Stop layout"), # stop button
  sigmajsOutput("sg")
) 

server <- function(input, output){

  output$sg <- renderSigmajs({
    sigmajs() %>%
      sg_nodes(nodes, id, size, color) %>%
      sg_edges(edges, id, source, target)
  })

  # start layout
  observeEvent(input$start, {
    sigmajsProxy("sg") %>% 
      sg_force_start_p() 
  })

  # stop layout
  observeEvent(input$stop, {
    sigmajsProxy("sg") %>% 
      sg_force_stop_p()
  })

}

shinyApp(ui, server) # run
```

Now that you are familiar with proxies we can look at the more powerful ones; though you will see, you can use them just as easily! For that we'll scrap the previous buttons and go back to the basic shiny app we initially set up.

Let's put a button that lets the user add nodes to the graph. For this example we'll only plot nodes, no edges.

```{r, eval = FALSE}
library(shiny)
library(sigmajs)

# initial nodes
nodes <- sg_make_nodes()

# nodes to add on click
nodes2add <- sg_make_nodes()
nodes2add$id <- 11:20 # ids must be unique

ui <- fluidPage(
  actionButton("add", "Add nodes"),
  sigmajsOutput("sg")
) 

server <- function(input, output){

  output$sg <- renderSigmajs({
    sigmajs() %>%
      sg_nodes(nodes, id, size, color) 
  })

  observeEvent(input$add, {
    sigmajsProxy("sg") %>%
      sg_add_nodes_p(nodes2add, id, size, color)
  })
}

shinyApp(ui, server) # run
```

*This is a simplified version of the `demo("add-nodes", package = "sigmajs")`*

It's fairly simple when you look at it.

1. We generate additional nodes.
2. We make sure that these additional nodes do not have the same `id` as the already existing nodes.
3. We add them using `sg_add_nodes_p` which acutally works just like `sg_nodes`.

## Events

Another great thing the package lets you do is capture how the user interact with your app. Then again there is a demo for the latter: `custom-events`.

